---
title: "PSE in Trust - supplementary materials"
author: "Ding-Cheng (Bruce) Peng"
email: "b.peng@auckland.ac.nz"
date: "July 2021"
output: html_document
---
# Session Setup
```{r}
library(checkpoint)
checkpoint(
  snapshotDate = "2020-10-01"
  , R.version = "3.6.2" # replaced with your version of R
  , checkpointLocation = "." # replaced with your own directory
)

rm(list = ls()); gc()
```


#Package and directory set up

```{r setup, include=FALSE}
# Load packages
if (!require(pacman)) install.packages('pacman')
pacman::p_load (sjstats, sjPlot, MuMIn, lme4, lmerTest, lattice, mediation, emmeans, 
                ggeffects, reshape, tidyverse, ggplot2, gridExtra, simr)

# Set working directory
setwd('C:/Users/dpen466/Google Drive/Phd (1)/PhD_writing/IPET_paper/Results/Analysis/PSE_trust_paper/')

# Source custom functions
source("Source/Helper_functions.R")

# ggplot colours
palette <- c("#eeaa7b", "#00b159", "#00aedb", "#F8766D", "#9590FF", "#CC9933", "#0000FF")
```

# Experiment 1
##Data setup
```{r}
# Loading data and transformation 
# Exp1.df <- read.csv('../IPET_fulldata_N=30.csv', header = T) %>% 
#                 # Remove missing data
#                 filter(complete.cases(Condition)) %>% 
#                 # Recode condition variable
#                 mutate(Condition = recode(Condition, '0' = 'Identify', '1' = 'Conceptual', '2' = 'Imagine'),
#                        Condition = relevel(as.factor(Condition), ref = 'Identify'),
#                        # Convert Scenario ID to factors
#                        Story_ID = as.factor(Story_ID),
#                        # Create dummy variables
#                        dummy_ident = as.numeric(Condition == 'Identify'),
#                        dummy_img = as.numeric(Condition == 'Imagine'),
#                        dummy_est = as.numeric(Condition == 'Conceptual'),
#                        # Within-cluster centering
#                        Coherence_C = group_center(Coherence.response, participant),
#                        Detail_C = group_center(Detail.response, participant),
#                        Help_C = group_center(help.response, participant),
#                        Trust_C = group_center(trust.response, participant))

# Create data with Estimate and Imagine helping conditons only
# Exp1_int <- Exp1.df %>%
#                    filter(Condition!='Identify')%>%
#                    mutate(Help_C = group_center(help.response,participant),
#                           Trust_C = group_center(trust.response, participant),
#                           Condition = droplevels(Condition),
#                           imgdet_int = dummy_img*Detail_C,
#                           imgcoh_int = dummy_img*Coherence_C)

# Models
load('Exp1.Rdata')
```

## Determine if clustering exists for story ID and participants for the two DVs
```{r}
# Willingness to help -- Model: ranova(lmer(help.response ~ (1|participant) + (1|Story_ID), data = Exp1.df)
VE1.1
#---------------------------------------------------------------------------------------------------------------
# Trust -- Model: ranova(lmer(trust.response~ (1|participant) + (1|Story_ID), data = Exp1.df)
VE1.2
```

## PSE in willingness to help and trust towards the person in need
```{r}
# Willingness to help
## Parsimonious model: lmer(help.response ~ Condition + (dummy_est + dummy_img|participant) + (1|Story_ID), data = Exp1.df)
## F-test with Kenward-Roger approximation of degress of freedom
anova(help_exp1, ddf = 'Kenward-Roger')
## Effect Size
r.squaredGLMM(help_exp1)
## Post hoc comparisons
posthoc_help1
confint(posthoc_help1)
#----------------------------------------------------------------------------------------------------------------------------
# Trust
## Parsimonious model: lmer(trust.response ~ Condition + (dummy_img|participant)+(dummy_img|Story_ID), data = Exp1.df)
## F-test with Kenward-Roger approximation of degress of freedom
anova(trust_exp1, ddf = 'Kenward-Roger')
## Effect Size
r.squaredGLMM(trust_exp1)
## Post hoc comparisons
posthoc_trust1
confint(posthoc_trust1)
```
#### Plots: Figure .....
```{r}
# Willingness to help
means_help1 <- data.frame(posthoc_help1$emmeans)
colnames(means_help1)[1] <- "Conditions"
bar_plot(means_help1, palette) + 
  scale_x_discrete(limits = c("Imagine", "Conceptual", "Identify"),
                   labels = c("Imagine Helping", "Conceptual Helping", "Identify Media Source")) +
  xlab ("Condition")
#------------------------------------------------------------------------------------------------------------------------
# Trust
means_trust1 <- data.frame(posthoc_trust1$emmeans)
colnames(means_trust1)[1] <- "Conditions"
bar_plot(means_trust1, palette) + 
  xlab ("Condition") + 
  scale_x_discrete(limits = c("Imagine", "Conceptual", "Identify"),
                   labels = c("Imagine Helping", "Conceptual Helping", "Identify Media Source")) +
  ylab ("Trust")
```


## Vividness by condition interactions
### Willingness to help
```{r}
# Detail -- Parsimonious model: lmer(help.response ~ Condition*Detail_C + (dummy_img + dummy_img:Detail_C|participant) + (1|Story_ID), data = Exp1_int)
# F-test using Kenward-Roger approximation of degress of freedom
anova(help_det_exp1, ddf = 'Kenward-Roger'); summary(help_det_exp1)
# Confidence intervals
confint(help_det_exp1, c("ConditionImagine", "Detail_C", "ConditionImagine:Detail_C"))
# Effect Size
r.squaredGLMM(help_det_exp1)
#-------------------------------------------------------------------------------------------------------------------------------------
# Coherence -- Parsimonious model: lmer (help.response ~ Condition*Coherence_C + (dummy_img|participant) + (Coherence_C|Story_ID), data = Exp1_int)
# F-test using Kenward-Roger approximation of degress of freedom
anova(help_coh_exp1, ddf = 'Kenward-Roger'); summary(help_coh_exp1)
# Confidence intervals
confint(help_coh_exp1, c("ConditionImagine", "Coherence_C", "ConditionImagine:Coherence_C"))
# Effect Size
r.squaredGLMM(help_coh_exp1)
```

### Trust 
```{r}
# Detail -- Parsimonious model: lmer(trust.response ~ Condition*Detail_C + (dummy_img + Detail_C|participant) + (1|Story_ID), data = Exp1_int)
# F-test using Kenward-Roger approximation of degress of freedom
anova(trust_det_exp1, ddf = 'Kenward-Roger'); summary(trust_det_exp1)
# Confidence intervals
confint(trust_det_exp1, c("ConditionImagine", "Detail_C", "ConditionImagine:Detail_C"))
# Effect Size
r.squaredGLMM(trust_det_exp1)
#---------------------------------------------------------------------------------------------------------------------------
# Coherence -- Parsimonious model: lmer(trust.response ~ Condition*Coherence_C + (dummy_img + Coherence_C|participant) + (0 + dummy_img|Story_ID), data = Exp1_int)
# F-test using Kenward-Roger approximation of degress of freedom
anova(trust_coh_exp1, ddf = 'Kenward-Roger'); summary(trust_coh_exp1)
# Confidence intervals
confint(trust_coh_exp1, c("ConditionImagine", "Coherence_C", "ConditionImagine:Coherence_C"))
# Effect Size
r.squaredGLMM(trust_coh_exp1)
```


### Plots: Figures...............
```{r}
# Willingness to help
## Detail: Figure
plot_det_help1 <- ggpredict(help_det_exp1, c("Detail_C[-4, 0, 4]", "Condition"))
det_help_plot1 <- int_plot(plot_det_help1, DV_name = 'Willingness to help', x_name = 'Detail', 
                           palette = c(palette[2], palette[3])) + 
                           theme(legend.position = "none")

## Coherence: Figure
plot_coh_help1 <- ggpredict(help_coh_exp1, c("Coherence_C[-4, 0, 4]", "Condition"))
coh_help_plot1 <- int_plot(plot_coh_help1, DV_name = 'Willingness to help', x_name = 'Coherence', 
                           palette = c(palette[2], palette[3])) + 
                           ylab('')

grid.arrange(det_help_plot1, coh_help_plot1, ncol = 2)
#----------------------------------------------------------------------------------------------------------------------------
# Trust
## Detail: Figure
plot_det_trust1 <- ggpredict(trust_det_exp1, c("Detail_C[-4, 0, 4]", "Condition"))
det_trust_plot1 <- int_plot(plot_det_trust1, DV_name = 'Trust', x_name = 'Detail', 
                           palette = c(palette[2], palette[3])) + 
                           theme(legend.position = "none")

## Coherence: Figure
plot_coh_trust1 <- ggpredict(trust_coh_exp1, c("Coherence_C[-4, 0, 4]", "Condition"))
coh_trust_plot1 <- int_plot(plot_coh_trust1, DV_name = 'Trust', x_name = 'Coherence', 
                            palette = c(palette[2], palette[3])) +
                            ylab('')

grid.arrange(det_trust_plot1, coh_trust_plot1, ncol = 2)
```
# Multilevel mediations 
## Condition -> Help -> Trust
```{r}
# Path a
## Model: lmer(help.response ~ Condition + (dummy_est + dummy_img|participant), data = Exp1.df)
summary(med.fit_exp1)

# Path b and c'
## Model: lmer(trust.response ~ Condition + Help_C + (Help_C|participant), data = Exp1.df)
summary(out.fit_exp1)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Mediaton models
## Identify vs Imagine
set.seed(67); med.out_0v2_exp1 <- mediate(med.fit_exp1, out.fit_exp1, 
                                          treat = 'Condition', mediator = 'Help_C', control.value = 'Identify',
                                          treat.value = 'Imagine', sims = 1e5)
summary(med.out_0v2_exp1)
## Conceptual vs Imagine
set.seed(67); med.out_1v2_exp1 <- mediate(med.fit_exp1, out.fit_exp1, 
                                          treat = 'Condition', mediator = 'Help_C', control.value = 'Conceptual',
                                          treat.value = 'Imagine', sims = 1e5)
summary(med.out_1v2_exp1)
```




# Experiment 2
## Data setup

```{r}
# Load personal norm of reciprocity questionnaire (PNQR) 
# Exp2.PNQR <- read.csv('../IPET2_PNRQ_Clean.csv', header = T) %>% 
#               mutate(
#                 # Create composite score for each component
#                 Belief = (Item1 + Item2 + Item3 + Item4 + Item5 + Item6 + Item7 + Item8)/8,
#                 Reciprocity_Neg = (Item10 + Item11 + Item12 + Item13 + Item14 + Item15 + Item16 + Item17 + Item18)/9,
#                 Reciprocity_Pos = (Item19 + Item20 + Item21 + Item22 + Item23 + Item24 + Item25 + Item26 + Item27)/9,
#                 # Grand mean centring for each participant
#                 Belief_C = Belief - mean(Belief,na.rm = T),
#                 Reciprocity_Neg_C = Reciprocity_Neg - mean(Reciprocity_Neg, na.rm = T),
#                 Reciprocity_Pos_C = Reciprocity_Pos - mean(Reciprocity_Pos, na.rm = T))

# Loading data and data Tranformation
# Exp2.df <- read.csv('../IPET2_fulldata_N=40.csv', header = T)
## Impute PNRQ Component scores into the main data set 
# start <- 1; PNRQ_n <- 1
# for (x in seq(32, 1200, by = 32)){
#   Exp2.df$Belief_C[start:x] <- rep(Exp2.PNQR$Belief_C[PNRQ_n], 32)
#   Exp2.df$Reciprocity_Neg_C[start:x] <- rep(Exp2.PNQR$Reciprocity_Neg_C[PNRQ_n], 32)
#   Exp2.df$Reciprocity_Pos_C[start:x] <- rep(Exp2.PNQR$Reciprocity_Pos_C[PNRQ_n], 32)
#   start <- x + 1;PNRQ_n <- PNRQ_n + 1
# }
# Exp2.df <- Exp2.df %>% 
#               # Remove missing data
#               filter(complete.cases(Condition)) %>%
#               # Recode condition variable
#               mutate(Condition = recode(Condition, '0' = 'Conceptual', '1' = 'Imagine'),
#                      Condition = relevel(as.factor(Condition), ref = 'Conceptual'),
#                      # Convert scenario ID to factors
#                      Story_ID = as.factor(Story_ID),
#                      # Create dummy variables
#                      dummy_img = as.numeric(Condition == 'Imagine'),
#                      # Within-cluster centering
#                      Coherence_C = group_center(Coherence, participant),
#                      Detail_C = group_center(Detail, participant),
#                      Help_C = group_center(Help, participant),
#                      Trust_C = group_center (Trust, participant),
#                      imgdet_int = dummy_img*Detail_C,
#                      imgcoh_int = dummy_img*Coherence_C)

# Models
load('Exp2.Rdata')
```

## Determine if clustering exist for story ID and participants for thee two DV
```{r}
# Willingness to help -- Model: ranova(lmer(Help ~ (1|participant) + (1|Story_ID), data = Exp2.df)
VE2.1
#---------------------------------------------------------------------------------------------------------------
# Trust -- Model: ranova(lmer(Trust~ (1|participant) + (1|Story_ID), data = Exp2.df)
VE2.2
```
## PSE in willingness to help and trust towards the person in need
```{r}
# Willingness to help
## Parsimonious model: lmer(Help ~ Condition + (dummy_img|participant) + (1|Story_ID), data = IPET2.df)
## F-test with Kenward-Roger approximation of degress of freedom
anova(help_exp2, ddf = 'Kenward-Roger')
## Effect Size
r.squaredGLMM(help_exp2)
## Post hoc comparisons
posthoc_help2
confint(posthoc_help2)
#---------------------------------------------------------------------------------------------------------------
# Trust
# Parsimonious model: lmer(Trust ~ Condition + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
## F-test with Kenward-Roger approximation of degress of freedom
anova(trust_exp2, ddf = 'Kenward-Roger')
## Effect Size
r.squaredGLMM(trust_exp2)
## Post hoc comparisons
posthoc_trust2
confint(posthoc_trust2)
```
#### Plots: Figure .....
```{r}
# Willingness to help
means_help2 <- data.frame(posthoc_help2$emmeans)
colnames(means_help2)[1] <- "Conditions"
ggplot(means_help2, aes(x = Conditions, y = emmean)) +
    geom_bar(stat = 'identity', width = 0.4, fill = c(palette[2], palette[3]), alpha = 0.5) +
    theme_minimal() +
    ylab("Willingness to help") +
    xlab ("Condition") +
    geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = .15, position = position_dodge(.9)) +
    coord_cartesian(ylim = c(1, 7)) + 
    expand_limits(y = c(1, 7)) + 
    scale_y_discrete(limits = c(1,2,3,4,5,6,7)) +
    theme_classic() +
    scale_x_discrete(limits = c("Imagine", "Conceptual"),
                     labels = c("Imagine Helping", "Conceptual Helping"))
#------------------------------------------------------------------------------------------------------------------------
# Trust
means_trust2 <- data.frame(posthoc_trust2$emmeans)
colnames(means_trust2)[1] <- "Conditions"
ggplot(means_trust2, aes(x = Conditions, y = emmean)) +
    geom_bar(stat = 'identity', width = 0.4, fill = c(palette[2], palette[3]), alpha = 0.5) +
    theme_minimal() +
    ylab("Trust") +
    xlab ("Condition") +
    geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = .15, position = position_dodge(.9)) +
    coord_cartesian(ylim = c(1, 7)) + 
    expand_limits(y = c(1, 7)) + 
    scale_y_discrete(limits = c(1,2,3,4,5,6,7)) +
    theme_classic() +
    scale_x_discrete(limits = c("Imagine", "Conceptual"),
                     labels = c("Imagine Helping", "Conceptual Helping"))
```


## Vividness by condition interactions
### Willingness to help
```{r}
# Detail -- Parsimonious model: lmer(Help ~ Condition*Detail_C + (dummy_img + Detail_C|participant) + (0 + dummy_img:Detail_C|participant) + (0 + dummy_img:Detail_C|Story_ID), data = Exp2.df)
# F-test using Kenward-Roger approximation of degress of freedom
anova(help_det_exp2, ddf = 'Kenward-Roger'); summary(help_det_exp2)
# Confidence intervals
confint(help_det_exp2, c("ConditionImagine", "Detail_C", "ConditionImagine:Detail_C"))
# Effect Size
r.squaredGLMM(help_det_exp2)
#------------------------------------------------------------------------------------------------------------------------
# Coherence -- Parsimonious model: lmer(Help ~ Condition*Coherence_C + (dummy_img + Coherence_C|participant) + (0 + dummy_img:Coherence_C|participant) + (1|Story_ID), data = Exp2.df)
# F-test using Kenward-Roger approximation of degress of freedom
anova(help_coh_exp2, ddf = 'Kenward-Roger'); summary(help_coh_exp2)
# Confidence intervals
confint(help_coh_exp2, c("ConditionImagine", "Coherence_C", "ConditionImagine:Coherence_C"))
# Effect Size
r.squaredGLMM(help_coh_exp2)
```

### Trust 
```{r}
# Detail -- Parsimonious model: lmer(Trust ~ Condition*Detail_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
# F-test using Kenward-Roger approximation of degress of freedom
anova(trust_det_exp2, ddf = 'Kenward-Roger'); summary(trust_det_exp2)
# Confidence intervals
confint(trust_det_exp2, c("ConditionImagine", "Detail_C", "ConditionImagine:Detail_C"))
# Effect Size
r.squaredGLMM(trust_det_exp2)
#------------------------------------------------------------------------------------------------------------------------
# Coherence -- Parsimonious model: lmer(Trust ~ Condition*Coherence_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
# F-test using Kenward-Roger approximation of degress of freedom
anova(trust_coh_exp2, ddf = 'Kenward-Roger'); summary(trust_coh_exp2)
# Confidence intervals
confint(trust_coh_exp2, c("ConditionImagine", "Coherence_C", "ConditionImagine:Coherence_C"))
# Effect Size
r.squaredGLMM(trust_coh_exp2)
```
### Plots: Figures...............
```{r}
# Willingness to help
## Detail: Figure
plot_det_help2 <- ggpredict(help_det_exp2, c("Detail_C[-4, 0, 4]", "Condition"))
det_help_plot2 <- int_plot(plot_det_help2, DV_name = 'Willingness to help', x_name = 'Detail', 
                           palette = c(palette[2], palette[3])) + 
                           theme(legend.position = "none")

## Coherence: Figure
plot_coh_help2 <- ggpredict(help_coh_exp2, c("Coherence_C[-4, 0, 4]", "Condition"))
coh_help_plot2 <- int_plot(plot_coh_help2, DV_name = 'Willingness to help', x_name = 'Coherence', 
                           palette = c(palette[2], palette[3])) +
                           ylab('')

grid.arrange(det_help_plot2, coh_help_plot2, ncol = 2)
#----------------------------------------------------------------------------------------------------------------------------
# Trust
## Detail: Figure
plot_det_trust2 <- ggpredict(trust_det_exp2, c("Detail_C[-4, 0, 4]", "Condition"))
det_trust_plot2 <- int_plot(plot_det_trust2, DV_name = 'Trust', x_name = 'Detail', 
                           palette = c(palette[2], palette[3])) + 
                           theme(legend.position = "none")

## Coherence: Figure
plot_coh_trust2 <- ggpredict(trust_coh_exp2, c("Coherence_C[-4, 0, 4]", "Condition"))
coh_trust_plot2 <- int_plot(plot_coh_trust2, DV_name = 'Trust', x_name = 'Coherence', 
                            palette = c(palette[2], palette[3])) +
                            ylab('')

grid.arrange(det_trust_plot2, coh_trust_plot2, ncol = 2)
```

# MLM Mediation analysis
## Condition -> Help -> Trust
```{r}
# Path a
## Model: lmer(Help ~ dummy_img + (dummy_img|participant), data = Exp2.df)
summary(med.fit_exp2)
# Path b and c'
## Model: lmer(Trust ~ dummy_img + Help_C + (dummy_img + Help_C|participant), data = Exp2.df)
summary(out.fit_exp2)
#------------------------------------------------------------------------------------------------------------------------
# Mediaton models
## Conceeptual vs Imagine
set.seed(67); med.out_exp2 <- mediate (med.fit_exp2, out.fit_exp2, 
                                           treat = 'dummy_img', mediator = 'Help_C', sims = 1e5)
summary(med.out_exp2)
```

# Cross-level interactions: PNRQ
```{r}
# Belief -- Model: lmer(Trust ~ Condition*Belief_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
# F-test using Kenward-Roger approximation of degress of freedom
anova(belief, ddf = 'Kenward-Roger'); summary(belief)
# Confidence intervals
confint(belief, c("ConditionImagine", "Belief_C", "ConditionImagine:Belief_C"))
# Effect Size
r.squaredGLMM(belief)
#------------------------------------------------------------------------------------------------------------------------
# Positive reciprocity -- Model: lmer(Trust ~ Condition*Reciprocity_Pos_C + (dummy_img|participant) + (dummy_img:Reciprocity_Pos_C|Story_ID), data = Exp2.df)
# F-test using Kenward-Roger approximation of degress of freedom
anova(pos_recip, ddf = 'Kenward-Roger'); summary(pos_recip)
# Confidence intervals
confint(pos_recip, c("ConditionImagine", "Reciprocity_Pos_C", "ConditionImagine:Reciprocity_Pos_C"))
# Effect Size
r.squaredGLMM(pos_recip)
#-----------------------------------------------------------------------------------------------------------------------
# Negative reciprocity -- Model: lmer(Trust ~ Condition*Reciprocity_Neg_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
# F-test using Kenward-Roger approximation of degress of freedom
anova(neg_recip, ddf = 'Kenward-Roger'); summary(neg_recip)
# Confidence intervals
confint(neg_recip, c("ConditionImagine", "Reciprocity_Neg_C", "ConditionImagine:Reciprocity_Neg_C"))
# Effect Size
r.squaredGLMM(neg_recip)
```
### Plots and power analyses: Figure....
```{r}
# Belief in reciprocity
ggpredict(belief, c("Condition", "Belief_C [-1.16, 0, 1.16]")) %>% plot() +
  theme_classic() +
  labs(title = "", y = "Trust", colour = "Belief in reciprocity") +
  scale_colour_brewer(palette = "Set1", labels = c("-1SD", "Mean", "+1SD")) +
  scale_x_discrete(limits = c("Conceptual helping", "Imagine helping"))

# Power analysis:
# m1 <- extend(belief, along = 'participant', n = 150)
# set.seed(67); pcurve_belief <- powerCurve(m1, test = fcompare(Trust ~ Condition + Belief_C), along = 'participant')
# set.seed(67); power_belief <- powerSim(belief, test = fcompare(Trust ~ Condition + Belief_C, method = 'kr'))
power_belief
## Power curve
plot(pcurve_belief)
#-------------------------------------------------------------------------------------------------
# Positive reciprocity
ggpredict(pos_recip, c("Condition", "Reciprocity_Pos_C [-1.15, 0, 1.15]")) %>% plot() +
  theme_classic() +
  labs(title = "", y = "Trust", colour = "Positive reciprocity") +
  scale_colour_brewer(palette = "Set1", labels = c("-1SD", "Mean", "+1SD")) +
  scale_x_discrete(limits = c("Conceptual helping", "Imagine helping")) 

# Power analysis
# m2 <- extend(pos_recip, along = 'participant', n = 150)
# set.seed(67); pcurve_posrecip <- powerCurve(m2, test = fcompare(Trust ~ Condition + Reciprocity_Pos_C), along = 'participant')
# set.seed(67); power_posrecip <- powerSim(pos_recip, test = fcompare(Trust ~ Condition + Reciprocity_Pos_C, method = 'kr'))
power_posrecip
## Power curve
plot(pcurve_posrecip)
```








