---
title: "PSE in Trust - supplementary materials"
author: "Ding-Cheng (Bruce) Peng"
email: "b.peng@auckland.ac.nz"
date: "July 2021"
output: html_document
---
# Session Setup
```{r}
library(checkpoint)
checkpoint(
  snapshotDate = "2020-10-01"
  , R.version = "3.6.2" # replaced with your version of R
  , checkpointLocation = "." # replaced with your own directory
)

rm(list = ls()); gc()
```


#Package and directory set up

```{r setup, include=FALSE}
# Load packages
if (!require(pacman)) install.packages('pacman')
pacman::p_load (sjstats, sjPlot, MuMIn, lme4, lmerTest, lattice, mediation, emmeans, ggeffects, reshape, tidyverse, ggplot2, gridExtra)

# Set working directory
setwd('C:/Users/dpen466/Google Drive/Phd (1)/PhD_writing/IPET_paper/Results/Analysis/PSE_trust_paper/')

# Source custom functions
source("Source/Helper_functions.R")

# ggplot colours
palette <- c("#eeaa7b", "#00b159", "#00aedb", "#F8766D", "#9590FF", "#CC9933", "#0000FF")
```

# Experiment 1
##Data setup
```{r}
# Loading data and transformation 
Exp1.df <- read.csv('../IPET_fulldata_N=30.csv', header = T) %>% 
                # Remove missing data
                filter(complete.cases(Condition)) %>% 
                # Recode condition variable
                mutate(Condition = recode(Condition, '0' = 'Identify', '1' = 'Conceptual', '2' = 'Imagine'),
                       Condition = relevel(as.factor(Condition), ref = 'Identify'),
                       # Convert Scenario ID to factors
                       Story_ID = as.factor(Story_ID),
                       # Create dummy variables
                       dummy_ident = as.numeric(Condition == 'Identify'),
                       dummy_img = as.numeric(Condition == 'Imagine'),
                       dummy_est = as.numeric(Condition == 'Conceptual'),
                       # Within-cluster centering
                       Coherence_C = group_center(Coherence.response, participant),
                       Detail_C = group_center(Detail.response, participant),
                       Help_C = group_center(help.response, participant),
                       Trust_C = group_center(trust.response, participant))

# Create data with Estimate and Imagine helping conditons only
Exp1_int <- Exp1.df %>%
                   filter(Condition!='Identify')%>%
                   mutate(Help_C = group_center(help.response,participant),
                          Trust_C = group_center(trust.response, participant),
                          Condition = droplevels(Condition),
                          imgdet_int = dummy_img*Detail_C,
                          imgcoh_int = dummy_img*Coherence_C)

# Models
# load('Exp1_models.Rdata')
```

## Determine if clustering exists for story ID and participants for the two DVs
```{r}
# Willingness to help -- Model: ranova(lmer(help.response ~ (1|participant) + (1|Story_ID), data = Exp1.df)
VE1.1 <- ranova(lmer(help.response ~ (1|participant) + (1|Story_ID), data = Exp1.df))
#---------------------------------------------------------------------------------------------------------------
# Trust 
VE1.2 <- ranova(lmer(trust.response ~ (1|participant) + (1|Story_ID), data = Exp1.df))
```

## PSE in willingness to help and trust towards the person in need
```{r}
# Willingness to help
## Parsimonious model: lmer(help.response ~ Condition + (dummy_est + dummy_img|participant) + (1|Story_ID), data = Exp1.df)
help_exp1 <- lmer(help.response ~ Condition + (dummy_est + dummy_img|participant) + (1|Story_ID), data = Exp1.df) #####
## F-test with Kenward-Roger approximation of degress of freedom
anova(help_exp1, ddf = 'Kenward-Roger')
## Effect Size
r.squaredGLMM(help_exp1)
## Post hoc comparisons
posthoc_help1 <- emmeans(help_exp1, pairwise ~ Condition, adjust = 'bonferroni') #####
posthoc_help1
confint(posthoc_help1)
#----------------------------------------------------------------------------------------------------------------------------
# Trust
## Parsimonious model: lmer(trust.response ~ Condition + (dummy_img|participant)+(dummy_img|Story_ID), data = Exp1.df)
trust_exp1 <- lmer(trust.response ~ Condition + (dummy_img|participant) + (dummy_img|Story_ID), data = Exp1.df)
## F-test with Kenward-Roger approximation of degress of freedom
anova(trust_exp1, ddf = 'Kenward-Roger')
## Effect Size
r.squaredGLMM(trust_exp1)
## Post hoc comparisons
posthoc_trust1 <- emmeans(trust_exp1, pairwise ~ Condition, adjust = 'bonferroni') #####
posthoc_trust1
confint(posthoc_help1)
```
#### Plots: Figure .....
```{r}
# Willingness to help
means_help1 <- data.frame(posthoc_help1$emmeans)
colnames(means_help1)[1] <- "Conditions"
bar_plot(means_help1, palette) + 
  scale_x_discrete(labels = c("Identify Media Source", "Conceptual Helping", "Imagine Helping")) +
  xlab ("Condition")
#------------------------------------------------------------------------------------------------------------------------
# Trust
means_trust1 <- data.frame(posthoc_trust1$emmeans)
colnames(means_trust1)[1] <- "Conditions"
bar_plot(means_trust1, palette) + 
  scale_x_discrete(labels = c("Identify Media Source", "Conceptual Helping", "Imagine Helping")) +
  xlab ("Condition") +
  ylab ("Trust")
```


## Vividness by condition interactions
### Willingness to help
```{r}
# Detail -- Parsimonious model: lmer(help.response ~ Condition*Detail_C + (dummy_img + dummy_img:Detail_C|participant) + (1|Story_ID), data = Exp1_int)
help_det_exp1 <- lmer(help.response ~ Condition*Detail_C + (dummy_img + dummy_img:Detail_C|participant) + (1|Story_ID),data = Exp1_int)
help_det_exp1 <- refit_LMM(help_det_exp1)
# Confidence intervals
confint(help_det_exp1, c("ConditionImagine", "Detail_C", "ConditionImagine:Detail_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(help_det_exp1, ddf = 'Kenward-Roger'); summary(help_det_exp1)
# Effect Size
r.squaredGLMM(help_det_exp1)
#-------------------------------------------------------------------------------------------------------------------------------------
# Coherence -- Parsimonious model: lmer (help.response ~ Condition*Coherence_C + (dummy_img|participant) + (Coherence_C|Story_ID), data = Exp1_int)
help_coh_exp1 <- lmer(help.response ~ Condition*Coherence_C + (dummy_img|participant) + (Coherence_C|Story_ID), data = Exp1_int)
# Confidence intervals
confint(help_coh_exp1, c("ConditionImagine", "Coherence_C", "ConditionImagine:Coherence_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(help_coh_exp1, ddf = 'Kenward-Roger'); summary(help_coh_exp1)
# Effect Size
r.squaredGLMM(help_coh_exp1)
```

### Trust 
```{r}
# Detail -- Parsimonious model: lmer(trust.response ~ Condition*Detail_C + (dummy_img + Detail_C|participant) + (0 + dummy_img|Story_ID), data = Exp1_int)
trust_det_exp1 <- lmer (trust.response ~ Condition*Detail_C + (dummy_img + Detail_C|participant) + (0 + dummy_img|Story_ID), data = Exp1_int)
trust_det_exp1 <- refit_LMM(trust_det_exp1) 
# Confidence intervals
confint(trust_det_exp1, c("ConditionImagine", "Detail_C", "ConditionImagine:Detail_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(trust_det_exp1, ddf = 'Kenward-Roger'); summary(trust_det_exp1)
# Effect Size
r.squaredGLMM(trust_det_exp1)
#---------------------------------------------------------------------------------------------------------------------------
# Coherence -- Parsimonious model: lmer(trust.response ~ Condition*Coherence_C + (dummy_img + Coherence_C|participant) + (0 + dummy_img|Story_ID), data = Exp1_int)
trust_coh_exp1 <- lmer (trust.response ~ Condition*Coherence_C + (dummy_img + Coherence_C|participant) + (0 + dummy_img|Story_ID), data = Exp1_int) 
trust_coh_exp1 <- refit_LMM(trust_coh_exp1)
# Confidence intervals
confint(trust_coh_exp1, c("ConditionImagine", "Coherence_C", "ConditionImagine:Coherence_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(trust_coh_exp1, ddf = 'Kenward-Roger'); summary(trust_coh_exp1)
# Effect Size
r.squaredGLMM(trust_coh_exp1)
```


### Plots: Figures...............
```{r}
# Willingness to help
## Detail: Figure
plot_det_help1 <- ggpredict(help_det_exp1, c("Detail_C[-4, 0, 4]", "Condition"))
det_help_plot1 <- int_plot(plot_det_help1, DV_name = 'Willingness to help', x_name = 'Detail', 
                           palette = c(palette[2], palette[3])) + 
                           theme(legend.position = "none")

## Coherence: Figure
plot_coh_help1 <- ggpredict(help_coh_exp1, c("Coherence_C[-4, 0, 4]", "Condition"))
coh_help_plot1 <- int_plot(plot_coh_help1, DV_name = 'Willingness to help', x_name = 'Coherence', 
                           palette = c(palette[2], palette[3]))  
                          #theme(legend.position = "none") +
                          #ylab('')

grid.arrange(det_help_plot1, coh_help_plot1, ncol = 2)
#----------------------------------------------------------------------------------------------------------------------------
# Trust
## Detail: Figure
plot_det_trust1 <- ggpredict(trust_det_exp1, c("Detail_C[-4, 0, 4]", "Condition"))
det_trust_plot1 <- int_plot(plot_det_trust1, DV_name = 'Trust', x_name = 'Detail', 
                           palette = c(palette[2], palette[3])) + 
                           theme(legend.position = "none")

## Coherence: Figure
plot_coh_trust1 <- ggpredict(trust_coh_exp1, c("Coherence_C[-4, 0, 4]", "Condition"))
coh_trust_plot1 <- int_plot(plot_coh_trust1, DV_name = 'Trust', x_name = 'Coherence', 
                            palette = c(palette[2], palette[3])) +
                            #theme(legend.position = "none") +
                            #ylab('')

grid.arrange(det_trust_plot1, coh_trust_plot1, ncol = 2)
```



# Multilevel mediations 
## Condition -> Help -> Trust
```{r}
# Path a
## Identify vs Imagine -- Model: lmer(help.response ~ dummy_est + dummy_img + (dummy_est + dummy_img|participant), data = Exp1.df)
med.fit_0v2_exp1 <- lmer(help.response ~ dummy_est + dummy_img + (dummy_est + dummy_img|participant), data = Exp1.df)
## Conceptual vs Imagine -- Model: lmer(help.response ~ dummy_ident + dummy_img + (dummy_img + dummy_ident|participant), data = Exp1.df)
med.fit_1v2_exp1 <- lmer(help.response ~ dummy_ident + dummy_img + (dummy_img + dummy_ident|participant), data = Exp1.df)
summary(med.fit_0v2_exp1); summary(med.fit_1v2_exp1)

# Path b and c'
## Identify vs Imagine -- Model: lmer(trust.response ~ dummy_est + dummy_img + Help_C + (Help_C|participant), data = Exp1.df)
out.fit_0v2_exp1 <- lmer(trust.response ~ dummy_est + dummy_img + Help_C + (Help_C|participant), data = Exp1.df)
## Conceptual vs Imagine -- Model: lmer(trust.response ~ dummy_ident + dummy_img + Help_C + (Help_C|participant), data = Exp1.df)
out.fit_1v2_exp1 <- lmer(trust.response ~ dummy_ident + dummy_img + Help_C + (Help_C|participant), data = Exp1.df)
summary(out.fit_0v2_exp1); summary(out.fit_1v2_exp1)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Mediaton models
## Identify vs Imagine
set.seed(67); med.out_0v2_exp1 <- mediate(med.fit_0v2_exp1, out.fit_0v2_exp1, 
                                          treat = 'dummy_img', mediator = 'Help_C', sims = 1e5)
summary(med.out_0v2_exp1); plot(med.out_0v2_exp1)
## Conceptual vs Imagine
set.seed(67); med.out_1v2_exp1 <- mediate(med.fit_1v2_exp1, out.fit_1v2_exp1, 
                                          treat = 'dummy_img', mediator = 'Help_C', sims = 1e5)
summary(med.out_1v2_exp1); plot(med.out_1v2_exp1)
```


# Multilevel moderated mediation 
## Vividness -> Help -> Trust
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#---------------------------------------------------------------------------------------------------------------------------
# Detail -- Models:
## Path a: lmer (help.response~dummy_img*Detail_C + (dummy_img + imgdet_int|participant), data = Exp1_int) 
med.fit_DH_exp1 <- lmer (help.response ~ dummy_img*Detail_C + (dummy_img + imgdet_int|participant), data = Exp1_int) 
## Path b and c': lmer (trust.response ~ dummy_img*(Detail_C + Help_C) + (Detail_C + Help_C|participant), data = Exp1_int)
out.fit_DH_exp1 <- lmer (trust.response ~ dummy_img*(Detail_C + Help_C) + (Detail_C + Help_C|participant), data = Exp1_int)

# Mediaton models
## Imagine helping
set.seed(67); Mod.Med_imgDH_exp1 <- mediate(med.fit_DH_exp1, out.fit_DH_exp1,
                                            covariates = list(dummy_img = 1), treat = "Detail_C", mediator = "Help_C", 
                                            sims = 1e5)
## Conceptual helping 
set.seed(67); Mod.Med_estDH_exp1 <- mediate(med.fit_DH_exp1, out.fit_DH_exp1, 
                                            covariates = list(dummy_img = 0), treat = "Detail_C", mediator = "Help_C", 
                                            sims = 1e5)
summary(Mod.Med_estDH_exp1); summary(Mod.Med_imgDH_exp1)

# Used to plot paths a & b for each condition 
est_DHa_exp1 <- lmer (help.response ~ Detail_C + (1|participant), data = subset(Exp1_int, Condition == 'Conceptual')) 
img_DHa_exp1 <- lmer (help.response ~ Detail_C + (Detail_C|participant),data = subset(Exp1_int, Condition == 'Imagine')) 
est_DHb_exp1 <- lmer (trust.response ~ Detail_C + Help_C + (Detail_C + Help_C|participant), 
                      data = subset(Exp1_int, Condition == 'Conceptual')) 
est_DHb_exp1 <- refit_LMM(est_DHb_exp1)
img_DHb_exp1 <- lmer (trust.response ~ Detail_C + Help_C + (Detail_C + Help_C|participant), 
                      data = subset(Exp1_int, Condition == 'Imagine'))
img_DHb_exp1 <- refit_LMM (img_DHb_exp1)
summary(est_DHa_exp1);summary(est_DHb_exp1);summary(img_DHa_exp1);summary(img_DHb_exp1)
#--------------------------------------------------------------------------------------------------------------------------
# Coherence -- Models:
## Path a: lmer(help.response ~ dummy_img*Coherence_C + (dummy_img|participant), data = Exp1_int) 
med.fit_CH_exp1 <- lmer(help.response ~ dummy_img*Coherence_C + (dummy_img|participant), data = Exp1_int) 
## Path b and c': lmer(trust.response ~ dummy_img*(Coherence_C + Help_C) + (Coherence_C + Help_C|participant), data = Exp1_int)
out.fit_CH_exp1 <- lmer(trust.response ~ dummy_img*(Coherence_C + Help_C) + (Coherence_C + Help_C|participant), 
                        data = Exp1_int)
summary(out.fit_CH_exp1)
# Mediaton models
## Imagine helping
set.seed(67); Mod.Med_imgCH_exp1 <- mediate(med.fit_CH_exp1, out.fit_CH_exp1,
                                            covariates = list(dummy_img = 1), treat = "Coherence_C", mediator = "Help_C",
                                            sims = 1e5)
## Conceptual helping 
set.seed(67); Mod.Med_estCH_exp1 <- mediate(med.fit_CH_exp1, out.fit_CH_exp1, 
                                            covariates = list(dummy_img = 0), treat = "Coherence_C", mediator = "Help_C",
                                            sims = 1e5)
summary(Mod.Med_estCH_exp1); summary(Mod.Med_imgCH_exp1)

# Used to plot paths a & b for each condition 
est_CHa_exp1 <- lmer (help.response ~ Coherence_C + (1|participant), data = subset(Exp1_int, Condition == 'Conceptual')) 
img_CHa_exp1 <- lmer (help.response ~ Coherence_C + (Coherence_C|participant), 
                      data = subset(Exp1_int, Condition == 'Imagine')) 
est_CHb_exp1 <- lmer (trust.response ~ Coherence_C + Help_C + (Coherence_C+Help_C|participant),
                      data = subset(Exp1_int, Condition == 'Conceptual')) 
est_CHb_exp1 <- refit_LMM(est_CHb_exp1)
img_CHb_exp1 <- lmer (trust.response ~ Coherence_C + Help_C + (Help_C|participant), 
                      data = subset(Exp1_int, Condition == 'Imagine'))
summary(est_CHa_exp1); summary(est_CHb_exp1); summary(img_CHa_exp1); summary(img_CHb_exp1)
```
### Plot: Figure...
```{r}
# Generate data file for ploting 
medmod_H_exp1.df <- cbind.data.frame("Vividness" = c('Detail', 'Detail', 'Coherence', 'Coherence'),
                                     "Condition" = c("Imagine Helping", 
                                                     "Conceptual Helping",
                                                     "Imagine Helping", 
                                                     "Conceptual Helping"), 
                                     "IE" = c(Mod.Med_imgDH_exp1$d0, 
                                              Mod.Med_estDH_exp1$d0, 
                                              Mod.Med_imgCH_exp1$d0, 
                                              Mod.Med_estCH_exp1$d0),
                                     "l_CI" = c(Mod.Med_imgDH_exp1$d0.ci[1], 
                                                Mod.Med_estDH_exp1$d0.ci[1], 
                                                Mod.Med_imgCH_exp1$d0.ci[1], 
                                                Mod.Med_estCH_exp1$d0.ci[1]), 
                                     "u_CI" = c(Mod.Med_imgDH_exp1$d0.ci[2], 
                                                Mod.Med_estDH_exp1$d0.ci[2], 
                                                Mod.Med_imgCH_exp1$d0.ci[2], 
                                                Mod.Med_estCH_exp1$d0.ci[2]))

# Detail
medmod_detH_plot1 <- medmod_plot(subset(medmod_H_exp1.df, Vividness == 'Detail'))
# Coherence
medmod_cohH_plot1 <- medmod_plot(subset(medmod_H_exp1.df, Vividness == 'Coherence'))

grid.arrange(medmod_detH_plot1, medmod_cohH_plot1, ncol = 2)
```

## Vividness -> Trust -> Help
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#----------------------------------------------------------------------------------------------------------------------------
# Detail -- Models:
## Path a: lmer(trust.response ~ dummy_img*Detail_C + (dummy_img + Detail_C|participant), data = Exp1_int)
med.fit_DT_exp1 <- lmer(trust.response ~ dummy_img*Detail_C + (dummy_img + Detail_C|participant), data = Exp1_int) 
## Path b and c': lmer(help.response ~ dummy_img*(Detail_C + Trust_C) + (dummy_img + Trust_C|participant), data = Exp1_int)
out.fit_DT_exp1 <- lmer(help.response~dummy_img*(Detail_C+Trust_C)+(dummy_img  +Trust_C|participant),data = Exp1_int)
out.fit_DT_exp1 <- refit_LMM(out.fit_DT_exp1)

# Mediaton models
## Imagine helping
set.seed(67); Mod.Med_imgDT_exp1 <- mediate(med.fit_DT_exp1, out.fit_DT_exp1,
                                            covariates = list(dummy_img = 1), treat = "Detail_C", mediator = "Trust_C",
                                            sims = 1e5)
# Conceptual helping
set.seed(67); Mod.Med_estDT_exp1 <- mediate(med.fit_DT_exp1, out.fit_DT_exp1, 
                                            covariates = list(dummy_img = 0), treat = "Detail_C", mediator = "Trust_C",
                                            sims = 1e5)
summary(Mod.Med_estDT_exp1); summary(Mod.Med_imgDT_exp1)

# Used to plot paths a & b for each condition 
est_DTa_exp1 <- lmer(trust.response ~ Detail_C + (1|participant), data = subset(Exp1_int, Condition == 'Conceptual')) 
img_DTa_exp1 <- lmer(trust.response ~ Detail_C + (Detail_C|participant), data = subset(Exp1_int, Condition == 'Imagine')) 
est_DTb_exp1 <- lmer(help.response ~ Detail_C + Trust_C + (Trust_C|participant),
                      data = subset(Exp1_int, Condition == 'Conceptual')) 
img_DTb_exp1 <- lmer(help.response ~ Detail_C + Trust_C + (Detail_C + Trust_C|participant), 
                     data = subset(Exp1_int, Condition == 'Imagine'))
summary(est_DTa_exp1); summary(est_DTb_exp1); summary(img_DTa_exp1); summary(img_DTb_exp1)
#----------------------------------------------------------------------------------------------------------------------------
# Coherence -- Models:
## Path a: lmer(trust.response~ dummy_img*Coherence_C + (Coherence_C|participant), data = Exp1_int) 
med.fit_CT_exp1 <- lmer(trust.response ~ dummy_img*Coherence_C + (Coherence_C|participant), data = Exp1_int) 
## Path b and c':lmer(help.response ~ dummy_img*(Coherence_C + Trust_C) + (dummy_img + Trust_C|participant), data = Exp1_int)
out.fit_CT_exp1 <- lmer (help.response ~ dummy_img*(Coherence_C + Trust_C) + (dummy_img + Trust_C|participant),
                         data = Exp1_int)

# Mediaton models
## Imagine helping
set.seed(67); Mod.Med_imgCT_exp1 <- mediate(med.fit_CT_exp1, out.fit_CT_exp1,
                                            covariates = list(dummy_img = 1), treat = "Coherence_C", mediator = "Trust_C",
                                            sims = 1e5)
## Conceptual helping 
set.seed(67); Mod.Med_estCT_exp1 <- mediate(med.fit_CT_exp1, out.fit_CT_exp1, 
                                            covariates = list(dummy_img = 0), treat = "Coherence_C", mediator = "Trust_C",
                                            sims = 1e5)
summary(Mod.Med_estCT_exp1); summary(Mod.Med_imgCT_exp1)

# Used to plot paths a & b for each condition 
est_CTa_exp1 <- lmer(trust.response ~ Coherence_C + (1|participant), data = subset(Exp1_int, Condition == 'Conceptual')) 
img_CTa_exp1 <- lmer(trust.response ~ Coherence_C + (1|participant), data = subset(Exp1_int, Condition == 'Imagine')) 
est_CTb_exp1 <- lmer(help.response ~ Coherence_C + Trust_C + (Trust_C|participant), 
                     data = subset(Exp1_int, Condition == 'Conceptual')) 
img_CTb_exp1 <- lmer(help.response ~ Coherence_C + Trust_C + (1|participant),
                     data = subset(Exp1_int, Condition == 'Imagine'))

summary(est_CTa_exp1); summary(est_CTb_exp1); summary(img_CTa_exp1); summary(img_CTb_exp1)
```
### Plot: Figure...
```{r}
# Generate data file for ploting 
medmod_T_exp1.df <- cbind.data.frame("Vividness" = c('Detail', 'Detail', 'Coherence', 'Coherence'),
                                     "Condition" = c("Imagine Helping", 
                                                     "Conceptual Helping",
                                                     "Imagine Helping", 
                                                     "Conceptual Helping"), 
                                     "IE" = c(Mod.Med_imgDT_exp1$d0, 
                                              Mod.Med_estDT_exp1$d0, 
                                              Mod.Med_imgCT_exp1$d0, 
                                              Mod.Med_estCT_exp1$d0),
                                     "l_CI" = c(Mod.Med_imgDT_exp1$d0.ci[1], 
                                                Mod.Med_estDT_exp1$d0.ci[1], 
                                                Mod.Med_imgCT_exp1$d0.ci[1], 
                                                Mod.Med_estCT_exp1$d0.ci[1]), 
                                     "u_CI" = c(Mod.Med_imgDT_exp1$d0.ci[2], 
                                                Mod.Med_estDT_exp1$d0.ci[2], 
                                                Mod.Med_imgCT_exp1$d0.ci[2], 
                                                Mod.Med_estCT_exp1$d0.ci[2]))

# Detail
medmod_detT_plot1 <- medmod_plot(subset(medmod_T_exp1.df, Vividness == 'Detail'))
# Coherence
medmod_cohT_plot1 <- medmod_plot(subset(medmod_T_exp1.df, Vividness == 'Coherence')) 
                               

grid.arrange(medmod_detT_plot1 + xlim(-0.1, 0.3), medmod_cohT_plot1 + xlim(-0.1, 0.3), ncol = 2)
```

# Experiment 2
## Data setup

```{r}
# Load personal norm of reciprocity questionnaire (PNQR) 
Exp2.PNQR <- read.csv('../IPET2_PNRQ_Clean.csv', header = T) %>% 
              mutate(
                # Create composite score for each component
                Belief = (Item1 + Item2 + Item3 + Item4 + Item5 + Item6 + Item7 + Item8)/8,
                Reciprocity_Neg = (Item10 + Item11 + Item12 + Item13 + Item14 + Item15 + Item16 + Item17 + Item18)/9,
                Reciprocity_Pos = (Item19 + Item20 + Item21 + Item22 + Item23 + Item24 + Item25 + Item26 + Item27)/9,
                # Grand mean centring for each participant
                Belief_C = Belief - mean(Belief,na.rm = T),
                Reciprocity_Neg_C = Reciprocity_Neg - mean(Reciprocity_Neg, na.rm = T),
                Reciprocity_Pos_C = Reciprocity_Pos - mean(Reciprocity_Pos, na.rm = T))

# Loading data and data Tranformation
Exp2.df <- read.csv('../IPET2_fulldata_N=40.csv', header = T)
## Impute PNRQ Component scores into the main data set 
start <- 1; PNRQ_n <- 1
for (x in seq(32, 1200, by = 32)){
  Exp2.df$Belief_C[start:x] <- rep(Exp2.PNQR$Belief_C[PNRQ_n], 32)
  Exp2.df$Reciprocity_Neg_C[start:x] <- rep(Exp2.PNQR$Reciprocity_Neg_C[PNRQ_n], 32)
  Exp2.df$Reciprocity_Pos_C[start:x] <- rep(Exp2.PNQR$Reciprocity_Pos_C[PNRQ_n], 32)
  start <- x + 1;PNRQ_n <- PNRQ_n + 1
}
Exp2.df <- Exp2.df %>% 
              # Remove missing data
              filter(complete.cases(Condition)) %>%
              # Recode condition variable
              mutate(Condition = recode(Condition, '0' = 'Conceptual', '1' = 'Imagine'),
                     Condition = relevel(as.factor(Condition), ref = 'Conceptual'),
                     # Convert scenario ID to factors
                     Story_ID = as.factor(Story_ID),
                     # Create dummy variables
                     dummy_img = as.numeric(Condition == 'Imagine'),
                     # Within-cluster centering
                     Coherence_C = group_center(Coherence, participant),
                     Detail_C = group_center(Detail, participant),
                     Help_C = group_center(Help, participant),
                     Trust_C = group_center (Trust, participant),
                     imgdet_int = dummy_img*Detail_C,
                     imgcoh_int = dummy_img*Coherence_C)
```

## Determine if clustering exist for story ID and participants for thee two DV
```{r}
# Help
VE2.1 <- ranova(lmer(Help ~ (1|participant) + (1|Story_ID), data = Exp2.df))
#---------------------------------------------------------------------------------------------------------------
# Trust 
VE1.2 <- ranova(lmer(Trust ~ (1|participant) + (1|Story_ID), data = Exp2.df))

# Determine if ordering of help and trust rating matters
summary(lmer(Help ~ help_trust + (1|participant) + (1|Story_ID), data = Exp2.df))
summary(lmer(Trust ~ help_trust + (1|participant) + (1|Story_ID), data = Exp2.df))
```
### PSE in willingness to help and trust towards the person in need
```{r}
# Willingness to help
## Parsimonious model: lmer(Help ~ Condition + (dummy_img|participant) + (1|Story_ID), data = IPET2.df)
help_exp2 <- lmer(Help ~ Condition + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
## F-test with Kenward-Roger approximation of degress of freedom
anova(help_exp2, ddf = 'Kenward-Roger')
## Effect Size
r.squaredGLMM(help_exp2)
## Post hoc comparisons
posthoc_help2 <- emmeans(help_exp2, pairwise ~ Condition, adjust = 'bonferroni') #####
posthoc_help2
confint(posthoc_help2)
#---------------------------------------------------------------------------------------------------------------
# Trust
# Parsimonious model: lmer(Trust ~ Condition + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
trust_exp2 <- lmer(Trust ~ Condition + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
## F-test with Kenward-Roger approximation of degress of freedom
anova(trust_exp2, ddf = 'Kenward-Roger')
## Effect Size
r.squaredGLMM(trust_exp2)
## Post hoc comparisons
posthoc_trust2 <- emmeans(trust_exp2, pairwise ~ Condition, adjust = 'bonferroni') #####
posthoc_trust2
confint(posthoc_trust2)
```
#### Plots: Figure .....
```{r}
# Willingness to help
means_help2 <- data.frame(posthoc_help2$emmeans)
colnames(means_help2)[1] <- "Conditions"
ggplot(means_help2, aes(x = Conditions, y = emmean)) +
    geom_bar(stat = 'identity', width = 0.4, fill = c(palette[2], palette[3]), alpha = 0.5) +
    theme_minimal() +
    ylab("Willingness to help") +
    xlab ("Condition") +
    geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = .15, position = position_dodge(.9)) +
    coord_cartesian(ylim = c(1, 7)) + 
    expand_limits(y = c(1, 7)) + 
    scale_y_discrete(limits = c(1,2,3,4,5,6,7)) +
    theme_classic() +
    scale_x_discrete(labels = c("Conceptual Helping", "Imagine Helping"))
#------------------------------------------------------------------------------------------------------------------------
# Trust
means_trust2 <- data.frame(posthoc_trust2$emmeans)
colnames(means_trust2)[1] <- "Conditions"
ggplot(means_trust2, aes(x = Conditions, y = emmean)) +
    geom_bar(stat = 'identity', width = 0.4, fill = c(palette[2], palette[3]), alpha = 0.5) +
    theme_minimal() +
    ylab("Trust") +
    xlab ("Condition") +
    geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = .15, position = position_dodge(.9)) +
    coord_cartesian(ylim = c(1, 7)) + 
    expand_limits(y = c(1, 7)) + 
    scale_y_discrete(limits = c(1,2,3,4,5,6,7)) +
    theme_classic() +
    scale_x_discrete(labels = c("Conceptual Helping", "Imagine Helping"))
```


## Vividness by condition interactions
### Willingness to help
```{r}
# Detail -- Parsimonious model: lmer(Help ~ Condition*Detail_C + (dummy_img + Detail_C|participant) + (0 + dummy_img:Detail_C|participant) + (Detail_C|Story_ID), data = Exp2.df)
help_det_exp2 <- lmer(Help ~ Condition*Detail_C + (dummy_img + Detail_C|participant) + (0 + dummy_img:Detail_C|participant) + (Detail_C|Story_ID), data = Exp2.df)
help_det_exp2 <- refit_LMM(help_det_exp2) #3 refits

# Confidence intervals
confint(help_det_exp2, c("ConditionImagine", "Detail_C", "ConditionImagine:Detail_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(help_det_exp2, ddf = 'Kenward-Roger'); summary(help_det_exp2)
# Effect Size
r.squaredGLMM(help_det_exp2)
#------------------------------------------------------------------------------------------------------------------------
# Coherence -- Parsimonious model: lmer(Help ~ Condition*Coherence_C + (dummy_img + Coherence_C|participant) + (0 + dummy_img:Coherence_C|participant) + (1|Story_ID), data = Exp2.df)
help_coh_exp2 <- lmer(Help ~ Condition*Coherence_C + (dummy_img + Coherence_C|participant) + (0 + dummy_img:Coherence_C|participant) + (1|Story_ID), data = Exp2.df)
# Confidence intervals
confint(help_coh_exp2, c("ConditionImagine", "Coherence_C", "ConditionImagine:Coherence_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(help_coh_exp2, ddf = 'Kenward-Roger'); summary(help_coh_exp2)
# Effect Size
r.squaredGLMM(help_coh_exp2)
```

### Trust 
```{r}
# Detail -- Parsimonious model: lmer(Trust ~ Condition*Detail_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
trust_det_exp2 <- lmer (Trust ~ Condition*Detail_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df) 
trust_det_exp2 <- refit_LMM(trust_fm_det)
# Confidence intervals
confint(trust_det_exp2, c("ConditionImagine", "Detail_C", "ConditionImagine:Detail_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(trust_det_exp2, ddf = 'Kenward-Roger'); summary(trust_det_exp2)
# Effect Size
r.squaredGLMM(trust_det_exp2)
#------------------------------------------------------------------------------------------------------------------------
# Coherence -- Parsimonious model: lmer(Trust ~ Condition*Coherence_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
trust_coh_exp2 <- lmer(Trust ~ Condition*Coherence_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
# Confidence intervals
confint(trust_coh_exp2, c("ConditionImagine", "Coherence_C", "ConditionImagine:Coherence_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(trust_coh_exp2, ddf = 'Kenward-Roger'); summary(trust_coh_exp2)
# Effect Size
r.squaredGLMM(trust_coh_exp2)
```
### Plots: Figures...............
```{r}
# Willingness to help
## Detail: Figure
plot_det_help2 <- ggpredict(help_det_exp2, c("Detail_C[-4, 0, 4]", "Condition"))
det_help_plot2 <- int_plot(plot_det_help2, DV_name = 'Willingness to help', x_name = 'Detail', 
                           palette = c(palette[2], palette[3])) + 
                           theme(legend.position = "none")

## Coherence: Figure
plot_coh_help2 <- ggpredict(help_coh_exp2, c("Coherence_C[-4, 0, 4]", "Condition"))
coh_help_plot2 <- int_plot(plot_coh_help2, DV_name = 'Willingness to help', x_name = 'Coherence', 
                           palette = c(palette[2], palette[3])) +
                           theme(legend.position = "none") +
                           ylab('')

grid.arrange(det_help_plot2, coh_help_plot2, ncol = 2)
#----------------------------------------------------------------------------------------------------------------------------
# Trust
## Detail: Figure
plot_det_trust2 <- ggpredict(trust_det_exp2, c("Detail_C[-4, 0, 4]", "Condition"))
det_trust_plot2 <- int_plot(plot_det_trust2, DV_name = 'Trust', x_name = 'Detail', 
                           palette = c(palette[2], palette[3])) + 
                           theme(legend.position = "none")

## Coherence: Figure
plot_coh_trust2 <- ggpredict(trust_coh_exp2, c("Coherence_C[-4, 0, 4]", "Condition"))
coh_trust_plot2 <- int_plot(plot_coh_trust2, DV_name = 'Trust', x_name = 'Coherence', 
                            palette = c(palette[2], palette[3])) +
                            theme(legend.position = "none") +
                            ylab('')

grid.arrange(det_trust_plot2, coh_trust_plot2, ncol = 2)
```

# MLM Mediation analysis
## Condition -> Help -> Trust
```{r}
# Path a
## Model: lmer(Help ~ dummy_img + (dummy_img|participant), data = Exp2.df)
med.fit_0v1_exp2 <- lmer(Help ~ dummy_img + (dummy_img|participant), data = Exp2.df)
summary(med.fit_0v1_exp2)
# Path b and c'
## Model: lmer(Trust ~ dummy_img + Help_C + (dummy_img + Help_C|participant), data = Exp2.df)
out.fit_0v1_exp2 <- lmer(Trust ~ dummy_img + Help_C + (dummy_img + Help_C|participant), data = Exp2.df)
summary(out.fit_0v1_exp2)
#------------------------------------------------------------------------------------------------------------------------
# Mediaton models
## Conceeptual vs Imagine
set.seed(67); med.out_0v1_exp2 <- mediate (med.fit_0v1_exp2, out.fit_0v1_exp2, treat = 'dummy_img', mediator = 'Help_C',
                                          sims = 1e5)
summary(med.out_0v1_exp2); plot(med.out_0v1_exp2)
```


# Multilevel moderated mediation 
## Vividness -> Help -> Trust
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#------------------------------------------------------------------------------------------------------------------------
# Detail -- Models:
## Path a: lmer(Help ~ dummy_img*Detail_C + (dummy_img + imgdet_int|participant), data = Exp2.df)  
med.fit_DH_exp2 <- lmer(Help ~ dummy_img*Detail_C + (dummy_img + imgdet_int|participant), data = Exp2.df)  
## Path b and c': lmer(Trust ~ dummy_img*(Detail_C + Help_C) + (dummy_img + Help_C|participant), data = Exp2.df)
out.fit_DH_exp2 <- lmer(Trust ~ dummy_img*(Detail_C + Help_C) + (dummy_img + Help_C|participant), data = Exp2.df)

summary(out.fit_DH_exp2)
# Mediaton models
## Imagine helping
set.seed(67); Mod.Med_imgDH_exp2 <- mediate(med.fit_DH_exp2, out.fit_DH_exp2,
                                            covariates = list(dummy_img = 1), treat = "Detail_C", mediator = "Help_C", 
                                            sims = 1e5)
## Conceptual helping 
set.seed(67); Mod.Med_estDH_exp2 <- mediate(med.fit_DH_exp2, out.fit_DH_exp2, 
                                            covariates = list(dummy_img = 0), treat = "Detail_C", mediator = "Help_C", 
                                            sims = 1e5)
summary(Mod.Med_estDH_exp2); summary(Mod.Med_imgDH_exp2)

# Used to plot paths a & b for each condition 
est_DHa_exp2 <- lmer(Help ~ Detail_C + (Detail_C|participant), data = subset(Exp2.df, Condition == 'Conceptual')) 
img_DHa_exp2 <- lmer(Help ~ Detail_C + (Detail_C|participant), data = subset(Exp2.df, Condition == 'Imagine')) 
est_DHb_exp2 <- lmer(Trust ~ Detail_C + Help_C + (Detail_C + Help_C|participant),
                     data = subset(Exp2.df, Condition == 'Conceptual')) 
est_DHb_exp2 <- refit_LMM(est_DHb_exp2)
img_DHb_exp2 <- lmer(Trust ~ Detail_C + Help_C + (Detail_C|participant), data = subset(Exp2.df, Condition == 'Imagine'))
summary(est_DHa_exp2); summary(est_DHb_exp2); summary(img_DHa_exp2); summary(img_DHb_exp2)
#------------------------------------------------------------------------------------------------------------------------
# Coherence -- Models:
## Path a: lmer(Help ~ dummy_img*Coherence_C + (dummy_img + imgcoh_int|participant), data = Exp2.df) 
med.fit_CH_exp2 <- lmer(Help ~ dummy_img*Coherence_C + (dummy_img + imgcoh_int|participant), data = Exp2.df)
## Path b and c': 
out.fit_CH_exp2 <- lmer(Trust ~ dummy_img*(Coherence_C + Help_C) + (dummy_img + Coherence_C + Help_C|participant),
                        data = Exp2.df)
out.fit_CH_exp2 <- refit_LMM(out.fit_CH_exp2)
# Mediaton models
## Imagine helping
set.seed(67); Mod.Med_imgCH_exp2 <- mediate(med.fit_CH_exp2, out.fit_CH_exp2,
                                            covariates = list(dummy_img = 1), treat = "Coherence_C", mediator="Help_C",
                                            sims = 1e5)
## Conceptual helping 
set.seed(67); Mod.Med_estCH_exp2 <- mediate(med.fit_CH_exp2, out.fit_CH_exp2, 
                                            covariates = list(dummy_img = 0), treat = "Coherence_C", mediator = "Help_C",
                                            sims = 1e5)
summary(Mod.Med_estCH_exp2); summary(Mod.Med_imgCH_exp2)

# Used to plot paths a & b for each condition 
est_CHa_exp2 <- lmer(Help ~ Coherence_C + (Coherence_C|participant),
                     data = subset(Exp2.df, Condition == 'Conceptual')) 
img_CHa_exp2 <- lmer(Help ~ Coherence_C + (Coherence_C|participant), data = subset(Exp2.df, Condition == 'Imagine')) 
est_CHb_exp2 <- lmer(Trust ~ Coherence_C + Help_C + (Coherence_C + Help_C|participant),
                      data = subset(Exp2.df, Condition == 'Conceptual'))
est_CHb_exp2 <- refit_LMM(est_CHb_exp2)
img_CHb_exp2 <- lmer(Trust ~ Coherence_C + Help_C + (Help_C|participant), 
                     data = subset(Exp2.df, Condition == 'Imagine'))
summary(est_CHa_exp2); summary(est_CHb_exp2); summary(img_CHa_exp2); summary(img_CHb_exp2)
```

### Plot: Figure...
```{r}
# Generate data file for ploting 
medmod_H_exp2.df <- cbind.data.frame("Vividness" = c('Detail', 'Detail', 'Coherence', 'Coherence'),
                                     "Condition" = c("Imagine Helping", 
                                                     "Conceptual Helping",
                                                     "Imagine Helping", 
                                                     "Conceptual Helping"), 
                                     "IE" = c(Mod.Med_imgDH_exp2$d0, 
                                              Mod.Med_estDH_exp2$d0, 
                                              Mod.Med_imgCH_exp2$d0, 
                                              Mod.Med_estCH_exp2$d0),
                                     "l_CI" = c(Mod.Med_imgDH_exp2$d0.ci[1], 
                                                Mod.Med_estDH_exp2$d0.ci[1], 
                                                Mod.Med_imgCH_exp2$d0.ci[1], 
                                                Mod.Med_estCH_exp2$d0.ci[1]), 
                                     "u_CI" = c(Mod.Med_imgDH_exp2$d0.ci[2], 
                                                Mod.Med_estDH_exp2$d0.ci[2], 
                                                Mod.Med_imgCH_exp2$d0.ci[2], 
                                                Mod.Med_estCH_exp2$d0.ci[2]))

# Detail
medmod_detH_plot2 <- medmod_plot(subset(medmod_H_exp2.df, Vividness == 'Detail'))
# Coherence
medmod_cohH_plot2 <- medmod_plot(subset(medmod_H_exp2.df, Vividness == 'Coherence'))

grid.arrange(medmod_detH_plot2 + xlim(0, 0.3), medmod_cohH_plot2 + xlim(0, 0.3), ncol = 2)
```
## Vividness -> Trust -> Help
```{r}
library(lmerTest)
detach (package:lmerTest, unload = T)
#----------------------------------------------------------------------------------------------------------------------------
# Detail -- Models:
## Path a: lmer(Trust ~ dummy_img*Detail_C + (dummy_img|participant), data = Exp2.df) 
med.fit_DT_exp2 <- lmer(Trust ~ dummy_img*Detail_C + (dummy_img|participant), data = Exp2.df) 
## Path b and c': lmer(Help ~ dummy_img*(Detail_C + Trust_C) + (dummy_img + Detail_C + Trust_C|participant), data = Exp2.df)
out.fit_DT_exp2 <- lmer(Help ~ dummy_img*(Detail_C + Trust_C) + (dummy_img + Detail_C + Trust_C|participant), 
                        data = Exp2.df)
out.fit_DT_exp2 <- refit_LMM(out.fit_DT_exp2)

# Mediaton models
## Imagine helping
set.seed(67); Mod.Med_imgDT_exp2 <- mediate(med.fit_DT_exp2, out.fit_DT_exp2,
                                            covariates = list(dummy_img = 1), treat = "Detail_C", mediator = "Trust_C",
                                            sims = 1e5)
## Conceptual helping 
set.seed(67); Mod.Med_estDT_exp2 <- mediate(med.fit_DT_exp2, out.fit_DT_exp2, 
                                            covariates = list(dummy_img = 0), treat = "Detail_C", mediator = "Trust_C",
                                            sims = 1e5)
summary(Mod.Med_estDT_exp2); summary(Mod.Med_imgDT_exp2)
#
# Used to plot paths a & b for each condition 
est_DTa_exp2 <- lmer(Trust ~ Detail_C + (Detail_C|participant), data = subset(Exp2.df, Condition == 'Conceptual')) 
img_DTa_exp2 <- lmer(Trust ~ Detail_C + (Detail_C|participant), data = subset(Exp2.df, Condition == 'Imagine'))  
img_DTa_exp2 <- refit_LMM(img_DTa_exp2)
est_DTb_exp2 <- lmer(Help ~ Detail_C + Trust_C + (Trust_C|participant), 
                     data = subset(Exp2.df, Condition == 'Conceptual'))
img_DTb_exp2 <- lmer(Help ~ Detail_C + Trust_C + (Detail_C + Trust_C|participant), 
                     data = subset(Exp2.df, Condition == 'Imagine'))
summary(est_DTa_exp2); summary(est_DTb_exp2); summary(img_DTa_exp2); summary(img_DTb_exp2)
#----------------------------------------------------------------------------------------------------------------------------
# Coherence -- Models:
## Path a: lmer (Trust ~ dummy_img*Coherence_C + (dummy_img + Coherence_C|participant), data = Exp2.df)
med.fit_CT_exp2 <- lmer (Trust ~ dummy_img*Coherence_C + (dummy_img + Coherence_C|participant), data = Exp2.df)
## Path b and c':lmer (Help ~ dummy_img*(Coherence_C + Trust_C) + (dummy_img + Coherence_C + Trust_C|participant), data = Exp2.df)
out.fit_CT_exp2 <- lmer (Help ~ dummy_img*(Coherence_C + Trust_C) + (dummy_img + Coherence_C + Trust_C|participant),
                         data = Exp2.df)

# Mediaton models
## Imagine helping
set.seed(67); Mod.Med_imgCT_exp2 <- mediate(med.fit_CT_exp2, out.fit_CT_exp2,
                                            covariates = list(dummy_img = 1), treat = "Coherence_C", mediator = "Trust_C",
                                            sims = 1e5)
## Conceptual helping 
set.seed(67); Mod.Med_estCT_exp2 <- mediate(med.fit_CT_exp2, out.fit_CT_exp2, 
                                            covariates = list(dummy_img = 0), treat = "Coherence_C", mediator = "Trust_C",
                                            sims = 1e5)
summary(Mod.Med_estCT_exp2); summary(Mod.Med_imgCT_exp2)

# Used to plot paths a & b for each condition 
est_CTa_exp2 <- lmer(Trust ~ Coherence_C + (1|participant), data = subset(Exp2.df, Condition == 'Conceptual')) 
img_CTa_exp2 <- lmer(Trust ~ Coherence_C + (1|participant),data = subset(Exp2.df, Condition == 'Imagine')) 
est_CTb_exp2 <- lmer(Help ~ Coherence_C + Trust_C + (Trust_C|participant), data = subset(Exp2.df, Condition == 'Conceptual'))
est_CTb_exp2 <- refit_LMM(est_CTb_exp2)
img_CTb_exp2 <- lmer(Help ~ Coherence_C + Trust_C + (1|participant), data = subset(Exp2.df, Condition == 'Imagine'))

summary(est_CTa_exp2); summary(est_CTb_exp2); summary(img_CTa_exp2); summary(img_CTb_exp2)
```
### Plot: Figure...
```{r}
# Generate data file for ploting 
medmod_T_exp2.df <- cbind.data.frame("Vividness" = c('Detail', 'Detail', 'Coherence', 'Coherence'),
                                     "Condition" = c("Imagine Helping", 
                                                     "Conceptual Helping",
                                                     "Imagine Helping", 
                                                     "Conceptual Helping"), 
                                     "IE" = c(Mod.Med_imgDT_exp2$d0, 
                                              Mod.Med_estDT_exp2$d0, 
                                              Mod.Med_imgCT_exp2$d0, 
                                              Mod.Med_estCT_exp2$d0),
                                     "l_CI" = c(Mod.Med_imgDT_exp2$d0.ci[1], 
                                                Mod.Med_estDT_exp2$d0.ci[1], 
                                                Mod.Med_imgCT_exp2$d0.ci[1], 
                                                Mod.Med_estCT_exp2$d0.ci[1]), 
                                     "u_CI" = c(Mod.Med_imgDT_exp2$d0.ci[2], 
                                                Mod.Med_estDT_exp2$d0.ci[2], 
                                                Mod.Med_imgCT_exp2$d0.ci[2], 
                                                Mod.Med_estCT_exp2$d0.ci[2]))

# Detail
medmod_detT_plot2 <- medmod_plot(subset(medmod_T_exp2.df, Vividness == 'Detail'))
# Coherence
medmod_cohT_plot2 <- medmod_plot(subset(medmod_T_exp2.df, Vividness == 'Coherence')) 
                               

grid.arrange(medmod_detT_plot2 + xlim(0, 0.2), medmod_cohT_plot2 + xlim(0, 0.2), ncol = 2)
```


## Cross-level interactions: PNRQ
```{r}
# Belief -- Model: lmer(Trust ~ Condition*Belief_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
belief <- lmer(Trust ~ Condition*Belief_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
# Confidence intervals
confint(belief, c("ConditionImagine", "Belief_C", "ConditionImagine:Belief_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(belief, ddf = 'Kenward-Roger'); summary(belief)
# Effect Size
r.squaredGLMM(belief)

emtrends(belief, pairwise ~ Condition, var = 'Belief_C')


sd <- sd(Exp2.PNQR$Belief_C)
m <- mean(Exp2.PNQR$Belief_C)
m - sd; m; m + sd
# plots
ggpredict(belief, c("Belief_C [-1.16, 0, 1.16]", "Condition"))%>% plot() +
  theme_classic() +
  labs(title = "", x="Belief in reciprocity", y = "Trust") 
  #scale_color_manual(values = c(palette[3], palette[4])) 
                     #labels = c("Imagine helping", "Conceptual helping")) 
#------------------------------------------------------------------------------------------------------------------------
# Positive reciprocity -- Model: lmer(Trust ~ Condition*Reciprocity_Pos_C + (dummy_img|participant) + (dummy_img:Reciprocity_Pos_C|Story_ID), data = Exp2.df)
pos_recip <- lmer(Trust ~ Condition*Reciprocity_Pos_C + (dummy_img|participant) + (dummy_img:Reciprocity_Pos_C|Story_ID),
                  data = Exp2.df)
# Confidence intervals
confint(pos_recip, c("ConditionImagine", "Reciprocity_Pos_C", "ConditionImagine:Reciprocity_Pos_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(pos_recip, ddf = 'Kenward-Roger'); summary(pos_recip)
# Effect Size
r.squaredGLMM(pos_recip)

emtrends(pos_recip, pairwise ~ Condition, var = 'Reciprocity_Pos_C')


ggpredict(pos_recip, c("Reciprocity_Pos_C", "Condition"))%>% plot() +
  theme_classic() +
  labs(title = "", x="Positive Reciprocity", y = "Trust") 
#-----------------------------------------------------------------------------------------------------------------------
# Negative reciprocity -- Model: lmer(Trust ~ Condition*Reciprocity_Neg_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
neg_recip <- lmer(Trust ~ Condition*Reciprocity_Neg_C + (dummy_img|participant) + (1|Story_ID), data = Exp2.df)
neg_recip <- refit_LMM(neg_recip)
# Confidence intervals
confint(neg_recip, c("ConditionImagine", "Reciprocity_Neg_C", "ConditionImagine:Reciprocity_Neg_C"))
# F-test using Kenward-Roger approximation of degress of freedom
anova(neg_recip, ddf = 'Kenward-Roger'); summary(neg_recip)
# Effect Size
r.squaredGLMM(neg_recip)
emtrends(neg_recip, pairwise ~ Condition, var = 'Reciprocity_Neg_C')
```






```{r}
m1 <- lmer(trust.response ~ Condition*Help_C + (1|participant) + (1|Story_ID), data = Exp1_int)
summary(m1)

m2 <- lmer(Trust ~ Condition*Help_C + (1|participant) + (1|Story_ID), data = Exp2.df)
summary(m2)
```







